How do we get from object recognition\\ to object naming?

### 2018-07-09 papers/SiVL2018/objectnaming.tex
some changes in section 2

%\cite{graf2016animal}
%\cite{Rosch1978}
%\subsection{Intro to Problem}
The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \textit{dog}'', ``the white \textit{dog} to the left'') and can be seen as a subtask of generating a referring expression. The lexical choice involved in naming is a non-trivial one \cite{brown1958shall}. Indeed, since an object is simultaneously a member of multiple categories (e.g., a young beagle is at once a dog, a beagle, an animal, a puppy etc.), all the various names that lexicalize these constitute a valid alternative: in fact, their denotation includes the target object. The study of object naming focuses on those factors that lead to the choice of a particular name in communicative situations. 
%These include properties of the object and candidate names, as well as contextual requirements.

@@

>>>>

%\cite{graf2016animal}
%\cite{Rosch1978}
%\subsection{Intro to Problem}

\subsection{Background}

The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \textit{dog}'', ``the white \textit{dog} to the left'') and can be seen as a subtask of generating a referring expression. The lexical choice involved in naming is a non-trivial one \cite{brown1958shall}. Indeed, since an object is simultaneously a member of multiple categories (e.g., a young beagle is at once a dog, a beagle, an animal, a puppy etc.), all the various names that lexicalize these constitute a valid alternative: in fact, their denotation includes the target object. The study of object naming focuses on those factors that lead to the choice of a particular name in communicative situations. 
%These include properties of the object and candidate names, as well as contextual requirements.

@@

\subsection{Previous Work}

As mentioned above, there is hardly any work on language \& vision that has studied object naming explicitily, on large-scale data sets. 
\cite{Ordonez:2016} investigate the problem of deriving appropriate object names, or so-called entry-level
 categories, from the output of an object recognizer. Their approach focusses on linking abstract object categories in ImageNet to actual words via various translation procedures. 
 Their performance is surprisingly low: around 35\% precision. We need to discuss this paper in more detail.
